\text{Additive drift with tail bounds}

### 2021-12-01 article.tex
fix explanations

\begin{align*}
    \limd \frac{\ln(N(d))}{\ln(G(d))} &= \limd \frac{\ln(\frac{d p(\gamma_m)}{s}  e^{-\gamma_m d})}{-\frac{d s}{2 c_m}} = \limd \frac{\ln(d) - \ln(s) + \ln(p(\gamma_m)) - \gamma_m d}{\frac{- d s}{2 c_m}} = \\
    &= \limd \frac{\ln(\mathcal{O}(\gamma_m)) - \gamma_m d}{\frac{- d s}{2 c_m}} = \limd \frac{\gamma_m d}{\frac{d s}{2 c_m}} = \limd \frac{2 c_m \gamma_m}{s} = \frac{2 \gamma_1 c_m}{s}
\end{align*}

@@

\begin{exmp}
    If \(s \to \frac{1}{\varepsilon}\) then \(\gamma_0, \gamma_1 \to 0\), but \(\delta_0\) decreases not so fast.

    If we take \(s = 1.03, \varepsilon = 1\), then \(c_m \approxeq 2.9\) and then:

    \begin{align*}
        \limd \frac{\ln(N(d))}{\ln(G(d))} \approxeq \frac{2}{3} < 1
    \end{align*}

>>>>

\begin{align*}
    \limd \frac{\ln(N(d))}{\ln(G(d))} &= \limd \frac{\ln(\frac{d p(\gamma_m)}{s}  e^{-\gamma_m d})}{-\frac{d s}{2 c_m}} = \limd \frac{\ln(d) - \ln(s) + \ln(p(\gamma_m)) - \gamma_m d}{\frac{- d s}{2 c_m}} = \\
    &= \limd \frac{\ln(\mathcal{O}(\gamma_m)) - \gamma_m d}{\frac{- d s}{2 c_m}} = \limd \frac{\gamma_m d}{\frac{d s}{2 c_m}} = \limd \frac{2 c_m \gamma_m}{s} = \frac{2 \gamma_1 c_m}{s} = \frac{2 \gamma_1}{\delta_0^m}
\end{align*}

Where \(\delta_0^m = \delta_0(c_m)\).

Obvious that \(\frac{\gamma_1}{\delta_0^m} \leq 1\) since by definition \(\delta_0^m \geq \gamma_1\). But is true that \(\frac{\gamma_1}{\delta_0^m} \geq \frac{1}{2}\) ?

Consider situation when math expectation in near zero. Then \(\gamma_0 \to 0\) and in some neighborhood of zero sub-gaussian boundary and expectation of exponent will behave as quadratic functions.

In this case denote:

\begin{align*}
    E[e^{\gamma \Delta_t}] \approxeq 1 + e_1 \gamma + \frac{e_2}{2} \gamma^2,
\end{align*}

where \(e_1 = E[\Delta_t],\ e_2 = E[\Delta_t^2]\).

And:

\begin{align*}
    e^{\frac{c \gamma^2}{2}} \approxeq 1 + \frac{c \gamma^2}{2}
\end{align*}

\begin{gather*}
    \gamma_1 = -\frac{2e_1}{e_2} \\
    \delta_0 = -\frac{2e_1}{e_2 - c}
\end{gather*}

But we must best \(\delta_0\), so we must find \(c_m\):

\begin{gather*}
    \delta_0^m = \frac{s}{c_m} \\
    -\frac{2e_1}{e_2 -c_m} = \frac{s}{c_m} \\
    c_m = \frac{s e_2}{s - 2e_1}
\end{gather*}

\begin{gather*} 
    \delta_0^m = \frac{2e_1}{e_2 - c_m} \\
    \delta_0^m = \frac{s - 2e_1}{e_2}
\end{gather*}

Ratio will be:

\begin{gather*}
    \frac{2 \gamma_1}{\delta_0^m} = 2 - \frac{2 s}{s - 2 e_1} \to 0
\end{gather*}

@@

\begin{exmp}

    If \(s \to \frac{1}{\varepsilon}\) then \(\gamma_0, \gamma_1 \to 0\), but \(\delta_0^m\) decreases not so fast.

    If we take \(s = 0.54, \varepsilon = 2\), then \(
        \delta_0^m \approxeq 0.55, \gamma_1 \approxeq 0.13\) and then:

    \begin{align*}
        \limd \frac{\ln(N(d))}{\ln(G(d))} \approxeq 0.473 < 1
    \end{align*}
